### 2019-02-01 spores-protocol-paper/sphinxes.tex
Adds copy of paper to spores-protocol-paper

\Textcite{Sphinx} designed \iac{UC} secure message format for mixes, called 
Sphinx.
Since it is \ac{UC} secure, it provably implements an ideal onion routing 
functionality.
\Ie, it provides bitwise unlinkability on the forward route, hides the path 
length, makes replies indistinguishable from forward messages and resists 
tagging attacks.
It is also compact with only 224 bytes of header for a five-hop path with 
128-bit security. \sonja{what about the CL properties?}
Sphinx only provides one node per onion layer; in this section we extend \ac{Sphinx} 
to \Sphinxes, which allows for multiple nodes per onion layer.
(See \cref{fig:OR-POR}.)
% AL: Bounded random-walk....
As such, \Sphinxes could be described as a bounded random-walk protocol, \ie the 
each node selects the next node from a set restricted by the source.

@@

We will now give an overview of the \ac{Sphinx} header format.
The idea is not to give a detailed description of \ac{Sphinx}, but to give the 
reader enough understanding of \ac{Sphinx} to understand the changes we make to 
achieve \Sphinxes.
For a more detailed understanding of Sphinx, we refer the reader to the 
description in the original Sphinx paper~\cite{Sphinx}.

@@

  \item \(\N\subset \bin^\kappa\) is a set of node identifiers.
    Each node \(n\in \N\) has a private key \(\sk_n\in \ZZ_q^*\) and a public 
    key \(\pk_n = g^{\sk_n}\in \G^*\).
    We assume that the identifier--public-key pairs, \((n, \pk_n)\), are 
    distributed.
    (Sphinx made a difference between nodes and destinations, \ie the set 
    \(\D\) such that \(\D\cap \N = \emptyset\) and \(\D\cup \N\) is prefix 
    free, see~\cite{Sphinx} for details.
    We could do the same adoption, but we do not need that for the purposes of 
    this paper.)
    We have two special node identifiers:
    \(\nullnode\in \N\) is the null-node identifier, indicating an empty 
    address.
    \(\rdvnode\in \N\) is the crossover-node identifier, indicating that the 
    current node is the node at the end of one leg of a route that needs to cross
   over to another, and that the payload is \iac{SPOR} route 
    for forwarding.

@@

This algorithm creates a header for \iac{SPOR}.
It is identical to that of \ac{Sphinx}~\cite[\S 3.2]{Sphinx} except that we use a 
set of addresses and keys for each layer instead of only one address and key.
Also, we do not distinguish between addresses of destinations and routers.

>>>>

\Textcite{Sphinx} designed \iac{UC} secure message format for mixes, called 
Sphinx.
Since it is \ac{UC} secure, it provably implements an ideal onion routing 
functionality.
\Ie, it provides bitwise unlinkability on the forward route, hides the path 
length, makes replies indistinguishable from forward messages and resists 
tagging attacks.
It is also compact with only 224 bytes of header for a five-hop path with 
128-bit security. \sonja{what about the CL properties?}
\Ac{Sphinx} only provides one node per onion layer; in this section we extend \ac{Sphinx} 
to \Sphinxes, which allows for multiple nodes per onion layer.
(See \cref{fig:OR-POR}.)
% AL: Bounded random-walk....
As such, \Sphinxes could be described as a bounded random-walk protocol, \ie the 
each node selects the next node from a set restricted by the source.

@@

We will now give an overview of the \ac{Sphinx} header format.
The idea is not to give a detailed description of \ac{Sphinx}, but to give the 
reader enough understanding of \ac{Sphinx} to understand the changes we make to 
achieve \Sphinxes.
For a more detailed understanding of \ac{Sphinx}, we refer the reader to the 
description in the original Sphinx paper~\cite{Sphinx}.

@@

  \item \(\N\subset \bin^\kappa\) is a set of node identifiers.
    Each node \(n\in \N\) has a private key \(\sk_n\in \ZZ_q^*\) and a public 
    key \(\pk_n = g^{\sk_n}\in \G^*\).
    We assume that the identifier--public-key pairs, \((n, \pk_n)\), are 
    distributed.
    (\Ac{Sphinx} made a difference between nodes and destinations, \ie the set 
    \(\D\) such that \(\D\cap \N = \emptyset\) and \(\D\cup \N\) is prefix 
    free, see~\cite{Sphinx} for details.
    We could do the same adoption, but we do not need that for the purposes of 
    this paper.)
    We have two special node identifiers:
    \(\nullnode\in \N\) is the null-node identifier, indicating an empty 
    address.
    \(\rdvnode\in \N\) is the crossover-node identifier, indicating that the 
    current node is the node at the end of one leg of a route that needs to cross
   over to another, and that the payload is \iac{SPOR} route 
    for forwarding.

@@

This algorithm creates a header for \iac{SPOR}.
It is identical to that of Sphinx~\cite[\S 3.2]{Sphinx} except that we use a 
set of addresses and keys for each layer instead of only one address and key.
Also, we do not distinguish between addresses of destinations and routers.
